Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/20-related-work.tex
Typo titre?

\subsection{Optical Character Recognition on historical texts}
Among the large amount of OCR solutions, being either open, free or paid software, available as libraries, Python packages, binaries or cloud API, not all options seem suitable for historical document processing.
We chose to avoid in our study paid and closed-source solutions.
This notably discards Transkribus~\cite{transkribus}, which relies on the commercial system ABBYY's Finereader as well as on two handwritten transcription engines, to process text.
% for Transkribus HTR engines, there is one closed source and one apparently open source
% we should test the open source one: https://github.com/jpuigcerver/pylaia

>>>>

\subsection{Optical Character Recognition of historical texts}
Among the large amount of OCR solutions, being either open, free or paid software, available as libraries, Python packages, binaries or cloud API, not all options seem suitable for historical document processing.
We chose to avoid in our study paid and closed-source solutions.
This notably discards Transkribus~\cite{transkribus}, which relies on the commercial system ABBYY's Finereader as well as on two handwritten transcription engines, to process text.
% for Transkribus HTR engines, there is one closed source and one apparently open source
% we should test the open source one: https://github.com/jpuigcerver/pylaia
